Advances in Artificial Intelligence for Data Visualization: Automated Reading of Residual Plots with Computer Vision

### 2023-04-17 Milestone_presentation_2/Milestone_presentation_2/Untitled.Rmd
prettify the slides

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
library(tidyverse)
library(visage)
style_solarized_light(
  background_color = "#FFFFFF",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_color = "#000000",
  text_font_size = "1.0rem",
  colors = c(myblue = "#006DAE", mywhite = "#FFFFFF")
)
```

@@

.center[
# 🔍Regression diagnostics🔍
]

.pull-left-center-80[

@@

.pull-right-120[

@@

Most residual-based tests for particular types of departure are also sensitive to other types of departures (Cook and Weisberg 1982).

@@

.center[
# 🔍Regression diagnostics🔍
]

.pull-right-center-80[

@@

@@

While such rejections may be **statistically correct**, their **sensitivity** may render the results **impractical**.

**Minor defects** in the model are **unlikely** to have a **significant impact** and may be best disregarded for practical purposes.

Therefore, a key goal of **residual plot diagnostics** is to **identify** potential issues that could lead to **incorrect conclusions or errors in subsequent analyses**.

@@

.center[
# 💔False visual discoveries💔
]

.pull-left-center-80[

@@

@@

.pull-right-center-80[

```{r}
set.seed(10131)
mod$gen_lineup(300, k = 20, pos = 8) %>%
  filter(null != FALSE) %>%
  bind_rows(ori_dat %>% mutate(k = 8, null = FALSE)) %>%
  VI_MODEL$plot_lineup(theme = theme_light(base_size = 12),
                       remove_grid_line = TRUE,
                       remove_axis = TRUE)
```
.center[
.caption[
Fig. 4: _Lineup of residual plots._
]
]

>>>>

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
library(tidyverse)
library(visage)
style_solarized_light(
  background_color = "#FFFFFF",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_color = "#000000",
  text_font_size = "1.0rem",
  header_h1_font_size = "2.0rem",
  colors = c(myblue = "#006DAE", mywhite = "#FFFFFF")
)
```

@@

.pull-left-center[

@@

# 🔍Regression diagnostics🔍

@@

Most residual-based tests for particular types of departure are also sensitive to **other types of departures** (Cook and Weisberg 1982).

@@

.pull-right-center[

@@

# 🔍Regression diagnostics🔍

@@

- While such rejections may be **statistically correct**, their **sensitivity** may render the results **impractical**. **Minor defects** in the model are **unlikely** to have a **significant impact** and may be best disregarded for practical purposes.

Residual plot diagnostics:
  - **Identify** potential issues that could lead to **incorrect conclusions or errors in subsequent analyses**.

@@

.pull-left-center[

@@

# 🤔False visual discoveries🤔

@@

If we embed the residual plot in a matrix of **null plots**, we will find the visual discovery is

.pull-right-center[

```{r}
set.seed(10131)
mod$gen_lineup(300, k = 20, pos = 8) %>%
  filter(null != FALSE) %>%
  bind_rows(ori_dat %>% mutate(k = 8, null = FALSE)) %>%
  VI_MODEL$plot_lineup(theme = theme_light(base_size = 12),
                       remove_grid_line = TRUE,
                       remove_axis = TRUE)
```
.center[
.caption[
Fig. 4: _A lineup of 20 residual plots of a simple linear regression. (Plot No.8 is Fig.3) Can you find the most different one?_
]
]
